---
title: "COPING_participation_analysis"
author: "Steven Bright"
date: "04/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Clean global environment}

remove(list = ls())

```

```{r Turn scientific notation off}

#Change it to "= 0" to turn it back on
options(scipen = 999)

```

#Call libraries

```{r Install packages}

#install.packages("broom")
#install.packages("knitr)
#install.packages("car")
#install.packages("rstatix")
#install.packages("pscl")
#install.packages("stargazer")
#install.packages("boot")
#install.packages("stats")
#install.packages("rcompanion")
#install.packages("MASS")
#install.packages("tidyverse")

```

```{r Load libraries}

library(broom)
library(knitr)
library(car)
library(rstatix)
library(pscl)
library(stargazer)
library(boot)
library(stats)
library(rcompanion)
library(MASS)
library(tidyverse)

```

#Read in data

```{r Source paths}
source("..//COPING_participation_paths.r")
```

```{r Source functions}
source("..//COPING_participation_functions.r")
```

```{r Read in glad coping participation data}
glad_coping_participation_raw <- read_rds(paste0(processed_data_path, processed_data_name))

#Check data
glad_coping_participation_raw %>% 
  head()
```

#Aim 1 Logistic regression model

Our first aim is to see whether participation in the COPING baseline is 
explained by the sociodemographic, mental and physical health characteristics
of the GLAD Study participants.

```{r Run complete LR model}
#Note: Have left out the "depressive_and_anxiety_comorbidity_labelled" variable
#because this is acting as the reference group for MH diagnoses.

complete_LR_model <- glm(
  formula = completed_baseline_labelled ~ age_cleaned + 
    gender_recode_labelled +
    highest_education_labelled +
    ethnicity_labelled +
    employment_labelled +
    partnership_status_labelled +
    phq.sum_score + 
    gad.sum_score +
    audit.sum_score +
    smoking_status_labelled +
    physical_health_comorbidities_labelled +
    MH_disorders_total_count +
    eating_disorders_labelled +
    OCRDs_labelled +
    psychotic_and_biploar_disorder_labelled +
    asd_labelled +
    ADHD_ADD_labelled +
    personality_disorder_labelled +
    PTSD_labelled +
    startDate + 
    kit_returned_labelled,
    #joined_coping_first_invitation_labelled,
  family = "binomial",
  data = glad_coping_participation_raw)

#Check output
summary(complete_LR_model)
```

```{r Calculate nagelkerke effect size}

complete_LR_model %>% 
  nagelkerke()

```

```{r Put complete LR model names into a vector}

#Put all LR variable names into vector in the order they appear in summary(model4)
complete_LR_model_names <- c(
  "Intercept",
  "age_cleaned",
  "gender_recode_labelledFemale",
  "gender_recode_labelledNon-binary/prefer to self-define",
  "highest_education_labelledA levels/AS levels or equivalent",
  "highest_education_labelledO levels/GCSEs or CSEs or equivalent",
  "highest_education_labelledNVQ or HND or HNC or equivalent",
  "highest_education_labelledNone of the above",
  "ethnicity_labelledMixed",
  "ethnicity_labelledAsian or Asian British",
  "ethnicity_labelledBlack or Black British",
  "ethnicity_labelledArab",
  "ethnicity_labelledOther",
  "employment_labelledRetired",
  "employment_labelledLooking after home and/or family",
  "employment_labelledUnable to work because of sickness or disability",
  "employment_labelledUnemployed",
  "employment_labelledDoing unpaid or voluntary work",
  "employment_labelledFull or part-time_student",
  "employment_labelledNone of the above",
  "partnership_status_labelledRelationship or married/civil partnership",
  "partnership_status_labelledDivorced/widowed/separated",
  "phq.sum_score",
  "gad.sum_score",
  "audit.sum_score",
  "smoking_status_labelledI smoke now",
  "smoking_status_labelledI used to smoke",
  "physical_health_comorbidities_labelled1 physical health disorder",
  "physical_health_comorbidities_labelled2+ physical health disorders",
  "MH_disorders_total_count",
  "eating_disorders_labelledEating disorder",
  "OCRDs_labelledOCRDs",
  "psychotic_and_biploar_disorder_labelledPsychotic and bipolar disorder",
  "psychotic_and_biploar_disorder_labelledOnly psychotic disorder",
  "psychotic_and_biploar_disorder_labelledOnly bipolar disorder",
  "asd_labelledAutistic spectrum disorder",
  "ADHD_ADD_labelledADHD or ADD disorder",
  "mhd.personality_disorder_labelledPersonality disorder",
  "PTSD_labelledPost-traumatic stress disorder",
  "startDate",
  "kit_returnedPt has provided saliva kit"
  #"joined_coping_first_invitationCompleted COPING baseline before 1st follow-up"
)

```

```{r Create tidy output for complete LR model}

#Create tidy model output
complete_LR_model_tidy <- tidy(
  complete_LR_model,
  exponentiate = T,
  conf.int = T) %>%
  mutate(
    Variable = complete_LR_model_names,
    Significance = if_else(
      p.value < 0.05, 
      1,
      0
      ) %>%
    recode_factor(
        "0" = "Not-significant",
        "1" = "Significant"
      )) %>%
  dplyr::select(
    Variable,
    OR = estimate,
    `CI 95% lower` = conf.low,
    `CI 95% upper` = conf.high,
     p.value,
    Significance
  ) %>% 
  mutate(
    adj.p.value = p.adjust(p.value, 
                           "bonferroni"),
    adj_significance = case_when(
        adj.p.value <= 0.001 ~ "***",
        adj.p.value <= 0.01 ~ "**",
        adj.p.value <= 0.05 ~ "*",
        adj.p.value > 0.05 ~ ""
      )
  )

complete_LR_model_tidy %>% 
  head(nrow(complete_LR_model_tidy))

#Create kable output
#complete_LR_model_kable <- kable(complete_LR_model_tidy[-c(1), ],
#      digits = 2)

```

```{r Extract odds ratios and CI's}
#Get OR's and CI's for explanatory variables
or_CI <- round(exp(cbind(coef(complete_LR_model), 
                         confint(complete_LR_model))), 
               digits=3) %>% 
  as.data.frame()

#Create variable column with variable names
or_CI <- or_CI %>% 
  mutate(variable=rownames(or_CI)) # extract the variables from rownames
  
#Rename and reorder columns
or_CI <- or_CI %>% 
  rename("AOR" = "V1",
         "lower_bound" = "2.5 %",
         "upper_bound" = "97.5 %"
         ) %>% 
  select(
    variable,
    AOR,
    lower_bound,
    upper_bound
  )

or_CI
```

```{r Turn explanatory variable column into a factor for plot}
#Create levels vector for explanatory variable column
explanatory_variable_levels <- c(
  "(Intercept)",
  "Age",
  "Female",
  "Non-binary/prefer to self-define",
  "A levels/AS levels or equivalent",
  "GCSEs or CSEs or equivalent",
  "NVQ or HND or HNC or equivalent",
  "None of the above edu",
  "Mixed",
  "Asian or Asian British",
  "Black or Black British",
  "Arab",
  "Other",
  "Retired",
  "Looking after home and/or family",
  "Sickness or disabled",
  "Unemployed",
  "Doing unpaid or voluntary work",
  "Student",
  "None of the above employ",
  "Relationship or married",
  "Divorced/widowed/separated",
  "phq.sum_score",
  "gad.sum_score",
  "audit.sum_score",
  "I smoke now",
  "I used to smoke",
  "1 physical health disorder",
  "2+ physical health disorders",
  "MH_disorders_total_count",
  "Eating disorder",
  "OCRDs",
  "Psychotic and bipolar disorder",
  "Only psychotic disorder",
  "Only bipolar disorder",
  "ASD",
  "ADHD or ADD disorder",
  "Personality disorder",
  "PTSD",
  "startDate",
  "Pt has provided saliva kit"
)

or_CI <- or_CI %>% 
  mutate(variable = explanatory_variable_levels)

or_CI$variable <- factor(or_CI$variable,
                              levels = explanatory_variable_levels)

#Check output
or_CI
```

```{r Forest plot of LR results}
plot_logit_model <- or_CI %>% 
  slice(-1) %>% #remove row number 1 (The intercept) 
  ggplot(aes(x = variable, y = AOR)) +
  geom_point(shape = 15,
             size  = 1, 
             position = "dodge", 
             color="black") + 
  geom_errorbar(aes(ymin  = lower_bound,
                    ymax  = upper_bound),
                size  = 0.7,
                position = "dodge", 
                color= "#EFC10B") +
  labs(title = "LR of participation in the COPING baseline survey",
         x = "Explanatory variables",
       y = "Adjusted odds ratios with 95% CI") +
  coord_flip() + 
  scale_y_continuous(breaks = seq(0, 4, 0.5),
                     limits = c(0, 4)) +
  scale_x_discrete(limits = rev) +
  geom_hline(yintercept = 1, color = "red", size = 1) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(color = "black"),
        axis.text.y = element_text(colour = "black"),
         axis.ticks = element_line(color = "black"))

#Check plot
plot_logit_model
```

##Run exploratory LR models
###Without saliva kit variable

During the analysis, we began to think that it may be circular to include
a measure of participation (providing a saliva kit for the GLAD study) as 
a predictor of participation. Therefore, we want to re-run the LR model
without the saliva kit predictor to see to what extent this influences the 
results.

```{r Run exploratory LR model}

exploratory_LR_model <- glm(
  formula = completed_baseline_labelled ~ age_cleaned + 
    gender_recode_labelled +
    highest_education_labelled +
    ethnicity_labelled +
    employment_labelled +
    partnership_status_labelled +
    phq.sum_score + 
    gad.sum_score +
    audit.sum_score +
    smoking_status_labelled +
    physical_health_comorbidities_labelled +
    MH_disorders_total_count +
    eating_disorders_labelled +
    OCRDs_labelled +
    psychotic_and_biploar_disorder_labelled +
    asd_labelled +
    ADHD_ADD_labelled +
    personality_disorder_labelled +
    PTSD_labelled +
    startDate,
    #kit_returned_labelled,
    #joined_coping_first_invitation_labelled,
  family = "binomial",
  data = glad_coping_participation_raw)

#Check output
summary(exploratory_LR_model)

```

```{r Calculate nagelkerke effect size}

exploratory_LR_model %>% 
  nagelkerke()

```

```{r Put complete LR model names into a vector}

#Put all LR variable names into vector in the order they appear in summary(model4)
exploratory_LR_model_names <- c(
  "Intercept",
  "age_cleaned",
  "gender_recode_labelledFemale",
  "gender_recode_labelledNon-binary/prefer to self-define",
  "highest_education_labelledA levels/AS levels or equivalent",
  "highest_education_labelledO levels/GCSEs or CSEs or equivalent",
  "highest_education_labelledNVQ or HND or HNC or equivalent",
  "highest_education_labelledNone of the above",
  "ethnicity_labelledMixed",
  "ethnicity_labelledAsian or Asian British",
  "ethnicity_labelledBlack or Black British",
  "ethnicity_labelledArab",
  "ethnicity_labelledOther",
  "employment_labelledRetired",
  "employment_labelledLooking after home and/or family",
  "employment_labelledUnable to work because of sickness or disability",
  "employment_labelledUnemployed",
  "employment_labelledDoing unpaid or voluntary work",
  "employment_labelledFull or part-time_student",
  "employment_labelledNone of the above",
  "partnership_status_labelledRelationship or married/civil partnership",
  "partnership_status_labelledDivorced/widowed/separated",
  "phq.sum_score",
  "gad.sum_score",
  "audit.sum_score",
  "smoking_status_labelledI smoke now",
  "smoking_status_labelledI used to smoke",
  "physical_health_comorbidities_labelled1 physical health disorder",
  "physical_health_comorbidities_labelled2+ physical health disorders",
  "MH_disorders_total_count",
  "eating_disorders_labelledEating disorder",
  "OCRDs_labelledOCRDs",
  "psychotic_and_biploar_disorder_labelledPsychotic and bipolar disorder",
  "psychotic_and_biploar_disorder_labelledOnly psychotic disorder",
  "psychotic_and_biploar_disorder_labelledOnly bipolar disorder",
  "asd_labelledAutistic spectrum disorder",
  "ADHD_ADD_labelledADHD or ADD disorder",
  "mhd.personality_disorder_labelledPersonality disorder",
  "PTSD_labelledPost-traumatic stress disorder",
  "startDate"
  #"joined_coping_first_invitationCompleted COPING baseline before 1st follow-up"
)

```

```{r Create tidy output for complete LR model}

#Create tidy model output
exploratory_LR_model_tidy <- tidy(
  exploratory_LR_model,
  exponentiate = T,
  conf.int = T) %>%
  mutate(
    Variable = exploratory_LR_model_names,
    Significance = if_else(
      p.value < 0.05, 
      1,
      0
      ) %>%
    recode_factor(
        "0" = "Not-significant",
        "1" = "Significant"
      )) %>%
  select(
    Variable,
    OR = estimate,
    `CI 95% lower` = conf.low,
    `CI 95% upper` = conf.high,
     p.value,
    Significance
  ) %>% 
  mutate(
    adj.p.value = p.adjust(p.value, 
                           "bonferroni"),
    adj_significance = case_when(
        adj.p.value <= 0.001 ~ "***",
        adj.p.value <= 0.01 ~ "**",
        adj.p.value <= 0.05 ~ "*",
        adj.p.value > 0.05 ~ ""
      )
  )

exploratory_LR_model_tidy %>% 
  head(nrow(exploratory_LR_model_tidy))

```

###Providing kit as outcome
17/07/2022
After presenting the first draft of the paper to the GLAD analaysis team,
it was recommended that a model could be run to investigate what factors 
are associated with providing a saliva kit to the GLAD Study.

```{r Run LR model to invesitgate factors associated with providing a kit}
providing_kit_LR_model <- glm(
  formula = kit_returned_labelled ~ age_cleaned + 
    gender_recode_labelled +
    highest_education_labelled +
    ethnicity_labelled +
    employment_labelled +
    partnership_status_labelled +
    phq.sum_score + 
    gad.sum_score +
    audit.sum_score +
    smoking_status_labelled +
    physical_health_comorbidities_labelled +
    MH_disorders_total_count +
    depressive_and_anxiety_comorbidity_labelled +
    eating_disorders_labelled +
    OCRDs_labelled +
    psychotic_and_biploar_disorder_labelled +
    asd_labelled +
    ADHD_ADD_labelled +
    personality_disorder_labelled +
    PTSD_labelled +
    startDate,
  family = "binomial",
  data = glad_coping_participation_raw)

#Check output
summary(providing_kit_LR_model)
```

```{r Create vector of explanatory variables in providing a kit LR model}
providing_kit_LR_model_names <- c(
  "Intercept",
  "age_cleaned",
  "gender_recode_labelledFemale",
  "gender_recode_labelledNon-binary/prefer to self-define",
  "highest_education_labelledA levels/AS levels or equivalent",
  "highest_education_labelledO levels/GCSEs or CSEs or equivalent",
  "highest_education_labelledNVQ or HND or HNC or equivalent",
  "highest_education_labelledNone of the above",
  "ethnicity_labelledMixed",
  "ethnicity_labelledAsian or Asian British",
  "ethnicity_labelledBlack or Black British",
  "ethnicity_labelledArab",
  "ethnicity_labelledOther",
  "employment_labelledRetired",
  "employment_labelledLooking after home and/or family",
  "employment_labelledUnable to work because of sickness or disability",
  "employment_labelledUnemployed",
  "employment_labelledDoing unpaid or voluntary work",
  "employment_labelledFull or part-time_student",
  "employment_labelledNone of the above",
  "partnership_status_labelledRelationship or married/civil partnership",
  "partnership_status_labelledDivorced/widowed/separated",
  "phq.sum_score",
  "gad.sum_score",
  "audit.sum_score",
  "smoking_status_labelledI smoke now",
  "smoking_status_labelledI used to smoke",
  "physical_health_comorbidities_labelled1 physical health disorder",
  "physical_health_comorbidities_labelled2+ physical health disorders",
  "depressive_and_anxiety_comorbidity_labelledDepressive and anxiety disorder",
  "depressive_and_anxiety_comorbidity_labelledDepressive disorder only",
  "depressive_and_anxiety_comorbidity_labelledAnxiety disorder only",
  "MH_disorders_total_count",
  "eating_disorders_labelledEating disorder",
  "OCRDs_labelledOCRDs",
  "psychotic_and_biploar_disorder_labelledPsychotic and bipolar disorder",
  "psychotic_and_biploar_disorder_labelledOnly psychotic disorder",
  "psychotic_and_biploar_disorder_labelledOnly bipolar disorder",
  "asd_labelledAutistic spectrum disorder",
  "ADHD_ADD_labelledADHD or ADD disorder",
  "mhd.personality_disorder_labelledPersonality disorder",
  "PTSD_labelledPost-traumatic stress disorder",
  "startDate"
  )
```

```{r Create tidy output for providing a kit LR model}
#Create tidy model output
providing_kit_LR_model_tidy <- tidy(
  providing_kit_LR_model,
  exponentiate = T,
  conf.int = T) %>%
  mutate(
    Variable = providing_kit_LR_model_names,
    Significance = if_else(
      p.value < 0.05, 
      1,
      0
      ) %>%
    recode_factor(
        "0" = "Not-significant",
        "1" = "Significant"
      )) %>%
  select(
    Variable,
    OR = estimate,
    `CI 95% lower` = conf.low,
    `CI 95% upper` = conf.high,
     p.value,
    Significance
  ) %>% 
  mutate(
    adj.p.value = p.adjust(p.value, 
                           "bonferroni"),
    adj_significance = case_when(
        adj.p.value <= 0.001 ~ "***",
        adj.p.value <= 0.01 ~ "**",
        adj.p.value <= 0.05 ~ "*",
        adj.p.value > 0.05 ~ ""
      )
  )

#Check output
providing_kit_LR_model_tidy
```

#Test assumptions of complete LR model

Checking LR assumptions in R: 
http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/

##Multicollinearity

Check that all IVs are not highly correlated.

```{r Get VIF values of final model}

complete_LR_model_VIF <- complete_LR_model %>% 
  vif()

complete_LR_model_VIF

```

##Linearity

Check the relationship between the continuous predictor variables and the logit
of the DV. This can be inspected visually by creating scatterplots between each
predictor and the logit values.


Note: We have to remove values that have 0 because when you log transform
a variable, it throws an error if there are any 0's in the variable. See:
https://stackoverflow.com/questions/31177795/error-in-glm-in-r

```{r Remove observations that have 0 on the continuous variables}

glad_coping_participation_lin <- glad_coping_participation_raw %>% 
  filter(gad.sum_score != 0,
         phq.sum_score != 0,
         audit.sum_score != 0)

#Check new dimensions
glad_coping_participation_raw %>% 
  dim()

glad_coping_participation_lin %>% 
  dim()

```


```{r LR model with interaction terms for continuous variables}

linearity_model <- glm(
  formula = completed_baseline_labelled ~ age_cleaned*log(age_cleaned) +
    gad.sum_score*log(gad.sum_score) +
    phq.sum_score*log(phq.sum_score) +
    audit.sum_score*log(audit.sum_score),
  family = "binomial",
  data = glad_coping_participation_lin
)

linearity_model %>% 
  summary()

```

##Outliers

Anything > 1 is a cause for concern.

```{r Check cooks distance values in LR model}

plot(complete_LR_model,
     which = 4)

```

```{r Extract model results}

LR.model_data <- augment(complete_LR_model) %>% 
  mutate(index = 1:n())

#Check output
LR.model_data %>% 
  glimpse()

```

```{r Plot standardised residuals}

LR.model_data %>% 
  ggplot(aes(index, .std.resid)) +
  geom_point(aes(colour = completed_baseline_labelled), alpha = .5) +
  theme_minimal()

```

```{r Check standardised residuals > 3.3}

LR.model_data %>% 
  filter(abs(.std.resid) > 3.3)

```

#Aim 2: Zero-inflated negative binomial regression

For aim 2, we want to see which variables are associated with participating
in the COPING follow-up surveys. We will run a zero-inflated negative binomial
regression to test for this.

```{r Put ZINB explanatory variavles into a vector}
ZINB_variables <- c(
  "age_cleaned",  
    "gender_recode_labelled", 
    "highest_education_labelled",
    "ethnicity_labelled",
    "employment_labelled", 
    "partnership_status_labelled",
    "phq.sum_score",
    "gad.sum_score", 
    "audit.sum_score",
    "smoking_status_labelled",
    "physical_health_comorbidities_labelled",
    "MH_disorders_total_count",
    "eating_disorders_labelled",
    "OCRDs_labelled",
    "psychotic_and_biploar_disorder_labelled",
    "asd_labelled",
    "ADHD_ADD_labelled",
    "personality_disorder_labelled",
    "PTSD_labelled",
    "kit_returned_labelled"
    )
```

```{r Run ZINB model}
ZINB_model <- zeroinf.neg.binomial.estimates(
  outcome = "total_COPING_waves",
  explanatory_variables = ZINB_variables,
  data_set = "glad_coping_participation_raw",
  name = "ZINB_model"
)

#Check ZINB model output
ZINB_model %>% 
  head()
```

```{r Create a significance column for the ZINB model results}
#Rename p value column
ZINB_model <- ZINB_model %>% 
  rename("p_value" = "p value")

#Turn p value column to numeric type instead of character
ZINB_model$p_value <- as.numeric(ZINB_model$p_value)

#Create significance column with p values
ZINB_model <- ZINB_model %>% 
  mutate(
    significance = case_when(
        p_value <= 0.00128205128 ~ "Significant",
        p_value > 0.00128205128 ~ ""
      )
  )

#Check significance column
ZINB_model %>% 
  head()
```

```{r Extract odds ratios and CI's from ZINB model}
#Get OR's and CI's for explanatory variables
ZINB_model_or_CI <- ZINB_model %>% 
  filter(
    Part == "zero"
  ) %>% 
  select(
    "Independent_variable" = "Independent variable",
    Estimate,
    "CI_95_low" = "95% CI low",
    "CI_95_up" = "95% CI up"
  )

ZINB_model_or_CI
```

```{r Turn independent variable column into a factor for plot}
#Create levels vector for explanatory variable column
ZINB_explanatory_variable_levels <- c(
  "(Intercept)",
  "Age",
  "Female",
  "Non-binary/prefer to self-define",
  "A levels/AS levels or equivalent",
  "GCSEs or CSEs or equivalent",
  "NVQ or HND or HNC or equivalent",
  "None of the above edu",
  "Mixed",
  "Asian or Asian British",
  "Black or Black British",
  "Arab",
  "Other",
  "Retired",
  "Looking after home and/or family",
  "Sickness or disabled",
  "Unemployed",
  "Doing unpaid or voluntary work",
  "Student",
  "None of the above employ",
  "Relationship or married",
  "Divorced/widowed/separated",
  "phq.sum_score",
  "gad.sum_score",
  "audit.sum_score",
  "I smoke now",
  "I used to smoke",
  "1 physical health disorder",
  "2+ physical health disorders",
  "MH_disorders_total_count",
  "Eating disorder",
  "OCRDs",
  "Psychotic and bipolar disorder",
  "Only psychotic disorder",
  "Only bipolar disorder",
  "ASD",
  "ADHD or ADD disorder",
  "Personality disorder",
  "PTSD",
  "Pt has provided saliva kit"
)

ZINB_model_or_CI <- ZINB_model_or_CI %>% 
  mutate(Independent_variable = ZINB_explanatory_variable_levels)

ZINB_model_or_CI$Independent_variable <- factor(ZINB_model_or_CI$Independent_variable,
                              levels = ZINB_explanatory_variable_levels)

#Check output
ZINB_model_or_CI
```

```{r Forest plot of ZINB results}
plot_ZINB_model <- ZINB_model_or_CI %>% 
  slice(-1) %>% #remove row number 1 (The intercept) 
  ggplot(aes(x = Independent_variable, y = Estimate)) +
  geom_point(shape = 15,
             size  = 1, 
             position = "dodge", 
             color = "black") + 
  geom_errorbar(aes(ymin  = CI_95_low,
                    ymax  = CI_95_up),
                size  = 0.7,
                position = "dodge", 
                color= "#EFC10B") +
  labs(title = "ZINB model of participation in the COPING follow-up surveys",
         x = "Explanatory variables",
       y = "Adjusted rate ratios with 95% CI") +
  coord_flip() + 
  #scale_y_continuous(breaks = seq(0, 4, 0.5),
  #                   limits = c(0, 4)) +
  scale_x_discrete(limits = rev) +
  geom_hline(yintercept = 1, color = "red", size = 1) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5),
    axis.text.x = element_text(color = "black"),
        axis.text.y = element_text(colour = "black"),
         axis.ticks = element_line(color = "black"))

#Check plot
plot_ZINB_model
```

Pseudo r-squared 
- use Nagelkerke (Cragg and Uhler) in the output regression summary table
```{r ZINB model nagelkerke}
nagelkerke(ZINB_model)
```

```{r Get p-values of ZINB model}

ZINB_model_p_values <- parameters::p_value(ZINB_model)

#Remove all the rows referring to the negative binomial ("count") model
ZINB_model_p_values <- ZINB_model_p_values %>% 
  select(Parameter, p) %>% 
  filter(str_detect(Parameter, "zero_"))

#Check results
ZINB_model_p_values

```

```{r Adjust the ZINB model p-values for multiple testing}

adj_ZINB_p_values <- ZINB_model_p_values$p %>% 
  p.adjust("bonferroni")

#Add the adjusted p-values to the p-value model
ZINB_model_p_values <- cbind(ZINB_model_p_values,
                             adj_ZINB_p_values)

#Create a significant label variable based on the adjusted p-values
ZINB_model_p_values <- ZINB_model_p_values %>% 
  mutate(
    adj_significance = case_when(
        adj_ZINB_p_values <= 0.001 ~ "***",
        adj_ZINB_p_values <= 0.01 ~ "**",
        adj_ZINB_p_values <= 0.05 ~ "*",
        adj_ZINB_p_values > 0.05 ~ ""
      )
  ) %>% 
  select(
    Parameter,
    adj_significance,
    p,
    adj_ZINB_p_values
  )

#Check results
ZINB_model_p_values

```

```{r Get p-values of count part of ZINB model}

ZINB_model_count_p_values <- parameters::p_value(ZINB_model)

#Remove all the rows referring to the negative binomial ("count") model
ZINB_model_count_p_values <- ZINB_model_count_p_values %>% 
  select(Parameter, p) %>% 
  filter(str_detect(Parameter, "count_"))

#Check results
ZINB_model_count_p_values

```

```{r Adjust the ZINB model count p-values for multiple testing}

adj_ZINB_count_p_values <- ZINB_model_count_p_values$p %>% 
  p.adjust("bonferroni")

#Add the adjusted p-values to the p-value model
ZINB_model_count_p_values <- cbind(ZINB_model_count_p_values,
                             adj_ZINB_count_p_values)

#Create a significant label variable based on the adjusted p-values
ZINB_model_count_p_values <- ZINB_model_count_p_values %>% 
  mutate(
    adj_significance = case_when(
        adj_ZINB_p_values <= 0.001 ~ "***",
        adj_ZINB_p_values <= 0.01 ~ "**",
        adj_ZINB_p_values <= 0.05 ~ "*",
        adj_ZINB_p_values > 0.05 ~ ""
      )
  ) %>% 
  select(
    Parameter,
    adj_significance,
    p,
    adj_ZINB_count_p_values
  )

#Check results
ZINB_model_count_p_values

```

```{r Inspect tidy output from ZINB model}

stargazer(ZINB_model, 
          zero.component = FALSE, 
          type = "text")

```

##Exploratory ZINB model

In the same sense of the exploratory LR model, we want to run an exploratory
ZINB model without the sproviding a saliva kit variable to see if this influences
the results.

```{r Remove providing a saliva kit from the ZINB_variables}
exploratory_ZINB_variables <- ZINB_variables[ZINB_variables != "kit_returned_labelled"]
```

```{r Run exploratory ZINB model without saliva kit variable}
exploratory_ZINB_model <- zeroinf.neg.binomial.estimates(
  outcome = "total_COPING_waves",
  explanatory_variables = exploratory_ZINB_variables,
  data_set = "glad_coping_participation_raw",
  name = "ZINB_model"
)

#Check ZINB model output
exploratory_ZINB_model %>% 
  head()
```

```{r Exponentiate the zero-inflated coefficients}
exp(coef((exploratory_ZINB_model)))
```

```{r ZINB as percentage}
round((exp(coef(exploratory_ZINB_model))-1)*100)
```

Pseudo r-squared 
- use Nagelkerke (Cragg and Uhler) in the output regression summary table
```{r ZINB model nagelkerke}
nagelkerke(exploratory_ZINB_model)
```

```{r Calculate confidence intervals for ZINB model}
confint(exploratory_ZINB_model)
```

```{r Get p-values of exploratory ZINB model}

exploratory_ZINB_model_p_values <- parameters::p_value(exploratory_ZINB_model)

#Remove all the rows referring to the negative binomial ("count") model
exploratory_ZINB_model_p_values <- exploratory_ZINB_model_p_values %>% 
  select(Parameter, p) %>% 
  filter(str_detect(Parameter, "zero_"))

#Check results
exploratory_ZINB_model_p_values

```

```{r Adjust the exploratory ZINB model p-values for multiple testing}

adj_exploratory_ZINB_p_values <- exploratory_ZINB_model_p_values$p %>% 
  p.adjust("bonferroni")

#Add the adjusted p-values to the p-value model
exploratory_ZINB_model_p_values <- cbind(exploratory_ZINB_model_p_values,
                                         adj_exploratory_ZINB_p_values)

#Create a significant label variable based on the adjusted p-values
exploratory_ZINB_model_p_values <- exploratory_ZINB_model_p_values %>% 
  mutate(
    adj_significance = case_when(
        adj_exploratory_ZINB_p_values <= 0.001 ~ "***",
        adj_exploratory_ZINB_p_values <= 0.01 ~ "**",
        adj_exploratory_ZINB_p_values <= 0.05 ~ "*",
        adj_exploratory_ZINB_p_values > 0.05 ~ ""
      )
  ) %>% 
  select(
    Parameter,
    adj_significance,
    p,
    adj_exploratory_ZINB_p_values
  )

#Check results
exploratory_ZINB_model_p_values

```

```{r Get count p-values of exploratory ZINB model}

exploratory_ZINB_model_count_p_values <- parameters::p_value(exploratory_ZINB_model)

#Remove all the rows referring to the negative binomial ("count") model
exploratory_ZINB_model_count_p_values <- exploratory_ZINB_model_count_p_values %>% 
  select(Parameter, p) %>% 
  filter(str_detect(Parameter, "count_"))

#Check results
exploratory_ZINB_model_count_p_values

```

```{r Adjust the exploratory ZINB model p-values for multiple testing}

adj_exploratory_ZINB_count_p_values <- exploratory_ZINB_model_count_p_values$p %>% 
  p.adjust("bonferroni")

#Add the adjusted p-values to the p-value model
exploratory_ZINB_model_count_p_values <- cbind(exploratory_ZINB_model_count_p_values,
                                         adj_exploratory_ZINB_count_p_values)

#Create a significant label variable based on the adjusted p-values
exploratory_ZINB_model_count_p_values <- exploratory_ZINB_model_count_p_values %>% 
  mutate(
    adj_significance = case_when(
        adj_exploratory_ZINB_count_p_values <= 0.001 ~ "***",
        adj_exploratory_ZINB_count_p_values <= 0.01 ~ "**",
        adj_exploratory_ZINB_count_p_values <= 0.05 ~ "*",
        adj_exploratory_ZINB_count_p_values > 0.05 ~ ""
      )
  ) %>% 
  select(
    Parameter,
    adj_significance,
    p,
    adj_exploratory_ZINB_count_p_values
  )

#Check results
exploratory_ZINB_model_count_p_values

```

```{r Write ZINB_model results to csv file}
ZINB_model %>% 
  write_csv("../ZIMB_participation_results.csv")
```
