---
title: "COPING_participation_analysis"
author: "Steven Bright"
date: "04/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Clean global environment}

remove(list = ls())

```

```{r Turn scientific notation off}

#Change it to "= 0" to turn it back on
options(scipen = 999)

```

#Call libraries

```{r Install packages}

#install.packages("broom")
#install.packages("knitr)
#install.packages("car")
#install.packages("tidyverse")
#install.packages("rstatix")

```

```{r Load libraries}

library(broom)
library(knitr)
library(car)
library(rstatix)
library(tidyverse)

```

#Read in data

```{r Source paths}

source("..//COPING_participation_paths.r")

```

```{r Read in glad coping participation data}

glad_coping_participation_raw <- read_rds(paste0(processed_data_path, processed_data_name))

#Check data
glad_coping_participation_raw %>% 
  head()

```

#Create tables for chi2 tests

Sociodemographic variables:

Age (age groups)
Gender
Ethnicity
Education
Employment
Partnership status

```{r Run chi2 test for gender and participation in the COPING baseline}

#NOTE: Topher suggests running chi2 tests like this.

# gender_recode_baseline_participation_chi2_test <- glad_coping_participation_raw %>%
#   count(gender_recode, completed_baseline) %>%
#   spread(key = completed_baseline, value = n) %>%
#   select(-gender_recode) %>% 
#   chisq.test() %>%
#   glance() %>%
#   add_column(
#     Variable = "gender_recode", # Change variable name here -> use nice label
#     .before = 1)

```

```{r Run pairwise chi2 tests for gender and participation in the COPING baseline}

# pairwise_gender_chi2_tests <- glad_coping_participation_raw %>%
#   count(gender_recode, completed_baseline) %>%
#   spread(key = gender_recode, value = n) %>%
#   select(-completed_baseline) %>% 
#   pairwise_chisq_gof_test(
#     p.adjust.method = "BH"
#   ) %>%
#   mutate(
#     Comparison = paste(group1,"vs.",group2, sep = " "),
#     Effect = p.adj.signif
#   ) %>%
#   select(
#     Comparison,
#     Effect
#   ) %>%
#   pivot_longer(
#     cols = c("Effect"),
#     values_to = "Difference") %>%
#   select(-name) %>%
#   pivot_wider(
#     names_from = "Comparison",
#     values_from = "Difference")

```

```{r Create contingency table for age}

age_groups_contingency_table <- table(glad_coping_participation_raw$age_groups_labelled,
                                      glad_coping_participation_raw$completed_baseline_labelled)

#Check output
age_groups_contingency_table

```

```{r Create contingency table for gender}

gender_contingency_table <- table(glad_coping_participation_raw$gender_recode_labelled,
                                  glad_coping_participation_raw$completed_baseline_labelled)

#Check output
gender_contingency_table

```

```{r Create contingency table for ethnicity}

ethnicity_contingency_table <- table(glad_coping_participation_raw$ethnicity_labelled,
                                     glad_coping_participation_raw$completed_baseline_labelled)

#Check output
ethnicity_contingency_table

```

```{r Create contingency table for Education}

education_contingency_table <- table(glad_coping_participation_raw$highest_education,
                                     glad_coping_participation_raw$completed_baseline_labelled)

#Check output
education_contingency_table

```

```{r Create contingency table for employment}

employment_contingency_table <- table(glad_coping_participation_raw$employment_labelled,
                                      glad_coping_participation_raw$completed_baseline_labelled)

#Check output
employment_contingency_table

```

```{r Partnership status}

partnership_contingency_table <- table(glad_coping_participation_raw$partnership_status_labelled,
                                       glad_coping_participation_raw$completed_baseline_labelled)

#Check output
partnership_contingency_table

```

#Run aim 1 chi2 tests

The aim here is to see whether there are any significant differences between 
the GLAD Study paticipants who did and did not take part in the COPING baseline.

##Age

```{r Chi2 test for age}

age_groups_chi2_test <- chisq.test(age_groups_contingency_table,
           correct = TRUE)

#Check output
age_groups_chi2_test

```

```{r Create post_hoc function for sig chi2 results}

post_hoc_chi2_func <- function(contingency_table, correct_adj = FALSE, sig_level = 0.05){
  
  #Get the adjusted residuals
  chi2_result <- chisq.test(contingency_table,
             correct = correct_adj)$stdres
  
  #Make Bonferonni correction
  print(bonferroni <- sig_level/(nrow(contingency_table) * ncol(contingency_table)))
  
  #Get critical z value
  print(qnorm(bonferroni/2))

  return(chi2_result)
  
}

```

```{r Run follow-up tests for age groups}

post_hoc_chi2_func(age_groups_contingency_table,
              correct_adj = TRUE)

```

##Gender

```{r Chi2 test for gender}

gender_chi2_test <- chisq.test(gender_contingency_table,
           correct = TRUE)

#Check output
gender_chi2_test

```

```{r Post hoc testing for gender}

post_hoc_chi2_func(gender_contingency_table,
              correct_adj = TRUE)

```

##Ethnicity

```{r Chi2 test for ethnicity}

ethnicity_chi2_test <- chisq.test(ethnicity_contingency_table,
           correct = TRUE)

#Check output
ethnicity_chi2_test

```

```{r Post-hoc testing for ethnicity chi2}

post_hoc_chi2_func(ethnicity_contingency_table,
                   correct_adj = TRUE)

```

##Education

```{r Chi2 test for education}

education_chi2_test <- chisq.test(education_contingency_table,
           correct = TRUE)

#Check output
education_chi2_test

```

```{r Post-hoc testing for education chi2 test}

post_hoc_chi2_func(education_contingency_table,
                   correct_adj = TRUE)

```

##Employment

```{r Chi2 test for employment}

employment_chi2_test <- chisq.test(employment_contingency_table,
           correct = TRUE)

#Check output
employment_chi2_test

```

```{r Post-hoc testing for employment chi2 test}

post_hoc_chi2_func(employment_contingency_table,
                   correct_adj = TRUE)

```

##Partnership status

```{r Chi2 test for partnership status}

partnership_chi2_test <- chisq.test(partnership_contingency_table,
           correct = TRUE)

#Check output
partnership_chi2_test

```

```{r Post-hoc testing for partnership status chi2 test}

post_hoc_chi2_func(partnership_contingency_table,
                   correct_adj = TRUE)

```

#Aim 1 Logistic regression model

Our first aim is to see whether participation in the COPING baseline is 
explained by the sociodemographic, mental and physical health characteristics
of the GLAD Study participants.

```{r Run complete LR model}

#Note: Have left out the "depressive_and_anxiety_comorbidity_labelled" variable
#because this is acting as the reference group for MH diagnoses.

complete_LR_model <- glm(
  formula = completed_baseline_labelled ~ age_cleaned + 
    gender_recode_labelled +
    highest_education_labelled +
    ethnicity_labelled +
    employment_labelled +
    partnership_status_labelled +
    phq.sum_score + 
    gad.sum_score +
    audit.sum_score +
    smoking_status_labelled +
    physical_health_comorbidities_labelled +
    MH_disorders_total_count +
    eating_disorders_labelled +
    OCRDs_labelled +
    psychotic_and_biploar_disorder_labelled +
    asd_labelled +
    ADHD_ADD_labelled +
    personality_disorder_labelled +
    startDate + 
    kit_returned_labelled +
    joined_coping_first_invitation_labelled,
  family = "binomial",
  data = glad_coping_participation_raw)

#Check output
summary(complete_LR_model)

```

```{r Put complete LR model names into a vector}

#Put all LR variable names into vector in the order they appear in summary(model4)
complete_LR_model_names <- c(
  "Intercept",
  "age_cleaned",
  "gender_recode_labelledFemale",
  "gender_recode_labelledNon-binary/prefer to self-define",
  "highest_education_labelledA levels/AS levels or equivalent",
  "highest_education_labelledO levels/GCSEs or equivalent",
  "highest_education_labelledCSEs or equivalent",
  "highest_education_labelledNVQ or HND or HNC or equivalent",
  "highest_education_labelledNone of the above",
  "ethnicity_labelledMixed",
  "ethnicity_labelledAsian or Asian British",
  "ethnicity_labelledBlack or Black British",
  "ethnicity_labelledArab",
  "ethnicity_labelledOther",
  "employment_labelledRetired",
  "employment_labelledLooking after home and/or family",
  "employment_labelledUnable to work because of sickness or disability",
  "employment_labelledUnemployed",
  "employment_labelledDoing unpaid or voluntary work",
  "employment_labelledFull or part-time_student",
  "employment_labelledNone of the above",
  "partnership_status_labelledRelationship or married/civil partnership",
  "partnership_status_labelledDivorced/widowed/separated",
  "phq.sum_score",
  "gad.sum_score",
  "audit.sum_score",
  "smoking_status_labelledI smoke now",
  "smoking_status_labelledI used to smoke",
  "physical_health_comorbidities_labelled1 physical health disorder",
  "physical_health_comorbidities_labelled2+ physical health disorders",
  "MH_disorders_total_count",
  "eating_disorders_labelledEating disorder",
  "OCRDs_labelledOCRDs",
  "psychotic_and_biploar_disorder_labelledPsychotic and bipolar disorder",
  "psychotic_and_biploar_disorder_labelledOnly psychotic disorder",
  "psychotic_and_biploar_disorder_labelledOnly bipolar disorder",
  "asd_labelledAutistic spectrum disorder",
  "ADHD_ADD_labelledADHD or ADD disorder",
  "mhd.personality_disorder_labelledPersonality disorder",
  "startDate",
  "kit_returnedPt has provided saliva kit",
  "joined_coping_first_invitationCompleted COPING baseline before 1st follow-up"
)

```

```{r Create tidy output for complete LR model}

#Create tidy model output
complete_LR_model_tidy <- tidy(
  complete_LR_model,
  exponentiate = T,
  conf.int = T) %>%
  mutate(
    Variable = complete_LR_model_names,
    Significance = if_else(
      p.value < 0.05, 
      1,
      0
      ) %>%
    recode_factor(
        "0" = "Not-significant",
        "1" = "Significant"
      )) %>%
  select(
    Variable,
    OR = estimate,
    `CI 95% lower` = conf.low,
    `CI 95% upper` = conf.high,
    `p value` = p.value,
    Significance
  )

complete_LR_model_tidy %>% 
  head(nrow(complete_LR_model_tidy))

#Create kable output
#complete_LR_model_kable <- kable(complete_LR_model_tidy[-c(1), ],
#      digits = 2)

```

#Test assumptions of complete LR model

Checking LR assumptions in R: 
http://www.sthda.com/english/articles/36-classification-methods-essentials/148-logistic-regression-assumptions-and-diagnostics-in-r/

##Multicollinearity

Check that all IVs are not highly correlated.

```{r Get VIF values of final model}

complete_LR_model_VIF <- complete_LR_model %>% 
  vif()

complete_LR_model_VIF

```

##Linearity

Check the relationship between the continuous predictor variables and the logit
of the DV. This can be inspected visually by creating scatterplots between each
predictor and the logit values.

```{r Predict the probability (p) of participating in COPING baseline}

COPING_baseline_probabilities <- complete_LR_model %>% 
  predict(type = "response")

#Create predicted COPING baseline case variable
predicted_COPING_baseline_cases <- ifelse(COPING_baseline_probabilities > 0.5,
                                          "positive",
                                          "negative")
#Check output
predicted_COPING_baseline_cases %>% 
  head()

```

```{r Create character vector with all the continuous predictors}

continuous_predictors <- c(
  "age_cleaned", 
  "phq.sum_score", 
  "gad.sum_score",
  "audit.sum_score"
    )

```

```{r Create data with no NAs on the LR predictors}

LR_predictors_without_NAs <- glad_coping_participation_raw %>% 
  select(
    age_cleaned, 
    gender_recode_labelled,
    highest_education_labelled,
    ethnicity_labelled,
    employment_labelled,
    partnership_status_labelled,
    phq.sum_score, 
    gad.sum_score,
    audit.sum_score,
    smoking_status_labelled,
    physical_health_comorbidities_labelled,
    mental_health_comorbidities_labelled,
    eating_disorders_labelled,
    OCRDs_labelled,
    psychotic_and_biploar_disorder_labelled,
    asd_labelled,
    ADHD_ADD_labelled,
    personality_disorder_labelled,
    startDate,
    kit_returned_labelled,
    joined_coping_first_invitation_labelled
  ) %>% 
  na.omit(.)

#Check rows match the predict model
COPING_baseline_probabilities %>% 
  length()

LR_predictors_without_NAs %>% 
  nrow()

```

```{r Prepare data for linearity plot}

#Select the continuous variables from the non-NA data
continuous_LR_predictors_without_NA <- LR_predictors_without_NAs %>% 
  select(all_of(continuous_predictors))

LR_linearity_check <- continuous_LR_predictors_without_NA %>% 
  mutate(logit = log(COPING_baseline_probabilities/(1-COPING_baseline_probabilities))) %>% 
  gather(key = "predictors", value = "predictor.value", -logit)

#Check output
LR_linearity_check %>% 
  glimpse()

```

```{r Create linearity scatterplots}

LR_linearity_check %>% 
  ggplot(aes(logit, predictor.value)) +
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "loess") +
  theme_minimal() +
  facet_wrap(~predictors, scales = "free_y")

```

Checking linearity for LR: (Old video)
https://www.youtube.com/watch?v=5TW_wWeTOe0

```{r Get quartiles and calculaties probabilities of completing baseline}

#Get age quartiles
age_quartiles <- summary(glad_coping_participation_raw$age_cleaned)

#Calculate probabilities of completing survey within each age quartile
age_q1_prob <- glad_coping_participation_raw %>% 
  filter(age_cleaned < 26) %>%
  pull(completed_baseline) %>% 
  mean(.)

age_q2_prob <- glad_coping_participation_raw %>% 
  filter(age_cleaned >= 26 & age_cleaned < 36) %>% 
  pull(completed_baseline) %>% 
  mean(.)

age_q3_prob <- glad_coping_participation_raw %>% 
  filter(age_cleaned >= 36 & age_cleaned < 49) %>% 
  pull(completed_baseline) %>% 
  mean(.)

age_q4_prob <- glad_coping_participation_raw %>% 
  filter(age_cleaned >= 49) %>% 
  pull(completed_baseline) %>% 
  mean(.)

#Check proportion is right
# glad_coping_participation_raw %>% 
#   filter(age_cleaned < 26) %>% 
#   group_by(completed_baseline) %>% 
#   count()

#Put probabilities into one object
age_cleaned_probs <- c(age_q1_prob, age_q2_prob, age_q3_prob, age_q4_prob)

```

```{r Plot completed baseline ~ age}

#Get logits
age_logits <- log(age_cleaned_probs/(1-age_cleaned_probs))

#Get medians
age_log_quartiles <- quantile(glad_coping_participation_raw$age_cleaned,
                              probs = seq(0, 1, 0.25))

age_q1_median <- glad_coping_participation_raw %>% 
  filter(age_cleaned < 26) %>% 
  pull(age_cleaned) %>% 
  median(.)

age_q2_median <- glad_coping_participation_raw %>% 
  filter(age_cleaned >= 26 &
           age_cleaned < 36) %>% 
  pull(age_cleaned) %>% 
  median(.)

age_q3_median <- glad_coping_participation_raw %>% 
  filter(age_cleaned >= 36 &
           age_cleaned < 49) %>% 
  pull(age_cleaned) %>% 
  median(.)

age_q4_median <- glad_coping_participation_raw %>% 
  filter(age_cleaned >= 49) %>% 
  pull(age_cleaned) %>% 
  median(.)

age_medians <- c(age_q1_median, age_q2_median, age_q3_median, age_q4_median)

```

```{r Make linear check plot for age}

plot(age_medians,
     age_logits,
     main = "Should look linear if age is linear with log age",
     xlab = "age",
     ylab = "log-odds(com base|age)",
     las = 1)

```

```{r Check linearity for sociodemographic model}

# boxTidwell(sociodemographic_LR_model$linear.predictors ~ age_cleaned,
#             data = glad_coping_participation_raw)

# sociodemographic_LR_linearity_test <- glm(
#   formula = completed_baseline ~ age_cleaned + age_cleaned * log(age_cleaned),
#   family = "binomial",
#   data = glad_coping_participation_raw)
# 
# #Check output
# summary(sociodemographic_LR_linearity_test)

```

##Outliers

Anything > 1 is a cause for concern.

```{r Check cooks distance values in LR model}

plot(complete_LR_model,
     which = 4)

```

```{r Extract model results}

LR.model_data <- augment(complete_LR_model) %>% 
  mutate(index = 1:n())

#Check output
LR.model_data %>% 
  glimpse()

```

```{r Plot standardised residuals}

LR.model_data %>% 
  ggplot(aes(index, .std.resid)) +
  geom_point(aes(colour = completed_baseline_labelled), alpha = .5) +
  theme_minimal()

```

```{r Check standardised residuals > 3.3}

LR.model_data %>% 
  filter(abs(.std.resid) > 3.3)

```

#Multiple Regression models

There are x4 models to run:

Model 1: Sociodemographic variables
Model 2: Psychiatric and health variables
Model 3: Study variables
Model 4: All variables together

##Model 1: Sociodemographic variables

```{r Run sociodemographic MLR model}

sociodemographic_MLR_model <- lm(total_COPING_waves ~ age_cleaned + 
    gender_recode_labelled +
    highest_education_labelled +
    ethnicity_labelled +
    employment_labelled +
    partnership_status_labelled,
    data = glad_coping_participation_raw)

#Check model output
summary(sociodemographic_MLR_model)

```

```{r Create tidy sociodemographic MLR model output}

#Create tidy model output
sociodemographic_MLR_model_tidy <- tidy(
  sociodemographic_MLR_model,
  conf.int = T) %>%
  mutate(
    Variable = sociodemographic_variable_names,
    Significance = if_else(
      p.value < 0.05, 
      1,
      0
      ) %>%
    recode_factor(
        "0" = "Not-significant",
        "1" = "Significant"
      )) %>%
  select(
    Variable,
    estimate,
    `CI 95% lower` = conf.low,
    `CI 95% upper` = conf.high,
    `p value` = p.value,
    Significance
  )

sociodemographic_MLR_model_tidy %>% 
  head(23)

#Create kable output
sociodemographic_MLR_model_kable <- kable(sociodemographic_MLR_model_tidy[-c(1), ],
      digits = 2)

```

##Model 2: Psychiatric and health variables

```{r Run psychiatric and health MLR model}

psychiatric_and_health_MLR_model <- lm(total_COPING_waves ~ phq.sum_score + 
    gad.sum_score +
    audit.sum_score +
    smoking_status_labelled +
    physical_health_comorbidities_labelled +
    mental_health_comorbidities_labelled +
    depressive_and_anxiety_comorbidity_labelled +
    eating_disorders_labelled +
    OCRDs_labelled +
    psychotic_and_biploar_disorder_labelled +
    autistic_spectrum_disorder +
    ADHD_ADD_labelled +
    personality_disorder_labelled,
  data = glad_coping_participation_raw)

#Check model output
summary(psychiatric_and_health_MLR_model)

```

```{r Create tidy output for psychiatric and health MLR}

#Create tidy model output
psychiatric_and_health_MLR_model_tidy <- tidy(
  psychiatric_and_health_MLR_model,
  exponentiate = T,
  conf.int = T) %>%
  mutate(
    Variable = psychiatric_and_health_LR_variable_names,
    Significance = if_else(
      p.value < 0.05, 
      1,
      0
      ) %>%
    recode_factor(
        "0" = "Not-significant",
        "1" = "Significant"
      )) %>%
  select(
    Variable,
    estimate,
    `CI 95% lower` = conf.low,
    `CI 95% upper` = conf.high,
    `p value` = p.value,
    Significance
  )

psychiatric_and_health_MLR_model_tidy %>% 
  head(14)

#Create kable output
psychiatric_and_health_MLR_model_kable <- kable(psychiatric_and_health_MLR_model_tidy[-c(1), ],
      digits = 2)

```

##Model 3: glad study variables model

```{r Run glad study variables MLR model}

glad_study_variables_MLR_model <- lm(
  formula = total_COPING_waves ~ startDate + 
    kit_returned_labelled +
    joined_coping_first_invitation_labelled,
  data = glad_coping_participation_raw)

#Check output
summary(glad_study_variables_MLR_model)

```

```{r Create tidy output for glad study variable MLR}

#Create tidy model output
glad_study_variables_MLR_model_tidy <- tidy(
  glad_study_variables_MLR_model,
  conf.int = T) %>%
  mutate(
    Variable = glad_study_LR_variable_names,
    Significance = if_else(
      p.value < 0.05, 
      1,
      0
      ) %>%
    recode_factor(
        "0" = "Not-significant",
        "1" = "Significant"
      )) %>%
  select(
    Variable,
    estimate,
    `CI 95% lower` = conf.low,
    `CI 95% upper` = conf.high,
    `p value` = p.value,
    Significance
  )

glad_study_variables_MLR_model_tidy %>% 
  head()

#Create kable output
glad_study_variables_MLR_model_kable <- kable(glad_study_variables_MLR_model_tidy[-c(1), ],
      digits = 2)

```

##Model 4: Complete MLR model

```{r Run complete MLR model}

complete_MLR_model <- lm(
  formula = completed_baseline ~ age_cleaned + 
    gender_recode_labelled +
    highest_education_labelled +
    ethnicity_labelled +
    employment_labelled +
    partnership_status_labelled +
    phq.sum_score +
    gad.sum_score +
    audit.sum_score +
    smoking_status_labelled +
    physical_health_comorbidities_labelled +
    mental_health_comorbidities_labelled +
    depressive_and_anxiety_comorbidity_labelled +
    eating_disorders_labelled +
    OCRDs_labelled +
    psychotic_and_biploar_disorder_labelled +
    autistic_spectrum_disorder +
    ADHD_ADD_labelled +
    personality_disorder_labelled +
    startDate + 
    kit_returned_labelled +
    joined_coping_first_invitation_labelled,
  data = glad_coping_participation_raw)

#Check output
summary(complete_MLR_model)

```

```{r Create tidy output for complete MLR model}

#Create tidy model output
complete_MLR_model_tidy <- tidy(
  complete_MLR_model,
  conf.int = T) %>%
  mutate(
    Variable = complete_LR_model_names,
    Significance = if_else(
      p.value < 0.05, 
      1,
      0
      ) %>%
    recode_factor(
        "0" = "Not-significant",
        "1" = "Significant"
      )) %>%
  select(
    Variable,
    estimate,
    `CI 95% lower` = conf.low,
    `CI 95% upper` = conf.high,
    `p value` = p.value,
    Significance
  )

complete_MLR_model_tidy %>% 
  head(46)

#Create kable output
complete_MLR_model_kable <- kable(complete_MLR_model_tidy[-c(1), ],
      digits = 2)

```

#Multiple linear regression assumptions

Linear regression assumptions:
https://thatdatatho.com/assumption-checking-for-multiple-linear-regression/

##Linearity

The second aim is to investigate whether any of the sociodemographic, psychiatric
and/or health factors explain any variance in the overall number of COPING follow-ups
the GLAD participant take part in.

```{r Create linear ggplot2 function}

linear_plot <- function(df, IV, DV){
  
  IV_data <- df[[IV]]
  IV_data_NA_removed <- IV_data %>% 
    na.omit()
  
  DV_data <- df[[DV]]
  DV_data_NA_removed <- DV_data %>% 
    na.omit()
  
  df %>% 
    ggplot(aes(y = DV_data, x = IV_data)) +
    geom_point(position = position_jitter(w = 0.1, h = 0.1),
            alpha = 0.3) +
  geom_smooth(method = lm, se = TRUE, col="black") +
    labs(y = DV,
        x = IV) +
    theme(panel.grid.major.y = element_line(size = 0.5,
                                        linetype = 'dashed',
                                        colour = "gray"),
        axis.text.x = element_text(colour="black", size = 12),
        axis.text.y = element_text(colour="black", size = 12),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank())

}

```

```{r Check Linear relationships between sociodemographic IVs and DV}

#Get IV variable names without Intercept and startDate
linear_relationship_vars <- glad_coping_participation_raw %>% 
  select(all_of(sociodemographic_variable_names)) %>% 
  colnames()

linear_relationship_vars %>% 
  map(linear_plot, 
      df = glad_coping_participation_raw,
      DV = "total_COPING_waves")

```

##Homoscedasticity

```{r Check VIF values for complete model}

sociodemographic_MLR_model %>% 
  vif()

```

##Diagnostic plots

```{r Create diagnostic plots for complete MLR model}

plot(sociodemographic_MLR_model, which = 1:4)

```
