---
title: "Tables_and_plots"
author: "Steven Bright"
date: "22/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Clean global environment}

remove(list = ls())

```

#Call libraries

```{r Install packages}

#install.packages("cowplot")
#install.packages("grid")
#install.packages("gridExtra")
#install.packages("gtsummary")
#install.packages("corrplot")
#install.packages("polycor")
#install.packages("tidyverse")

```

```{r Load libraries}

library(cowplot)
library(grid)
library(gridExtra)
library(gtsummary)
library(corrplot)
library(polycor)
library(tidyverse)

```

#Add colour palette

```{r Create colour palettes}

glad_colour <- "#EFC10B"
glad_coping_palette2 <- c("#EFC10B", "#B7DEE8")
glad_coping_palette3 <- c("#EFC10B", "#B7DEE8", "#0403ff")

```

#Source functions

```{r Source functions}

source("..//COPING_participation_functions.r")

```

#Source data paths

```{r Source paths}

source("..//COPING_participation_paths.r")

```

```{r Read in glad coping participation data}

glad_coping_participation <- read_rds(paste0(processed_data_path, processed_data_name))

#Check data
glad_coping_participation %>% 
  head()

```

#Create COPING survey completion graph
This graph will visualise the completion of the COPING surveys across the 
COPING study.

```{r Visualise distribution of COPING surveys completed}
glad_coping_participation %>% 
  group_by(total_COPING_waves) %>% 
  count()
```

```{r Get N participants for plot}
#Number or participants who completed baseline but no follow-up surveys
N_no_followups <- glad_coping_participation %>% 
  filter(completed_baseline == 1,
    total_COPING_waves == 0) %>% 
  nrow()

#Number of participants who completed baseline survey and at least one survey
N_followups <- glad_coping_participation %>% 
  filter(completed_baseline == 1,
         total_COPING_waves != 0) %>% 
  nrow()

#Check results
N_no_followups
N_followups
```

```{r Create total COPING waves variable with 0 responses level}
glad_coping_participation <- glad_coping_participation %>% 
  mutate(total_COPING_waves_with0 = 
           case_when(
             #This find the N pt's who didn't complete any follow-ups after joining COPING
             total_COPING_waves == 0 &
               completed_baseline == 1 ~ 0,
             
             #Leave the other values as they are
             total_COPING_waves == 1 ~ 1,
             total_COPING_waves == 2 ~ 2,
             total_COPING_waves == 3 ~ 3,
             total_COPING_waves == 4 ~ 4,
             total_COPING_waves == 5 ~ 5,
             total_COPING_waves == 6 ~ 6,
             total_COPING_waves == 7 ~ 7,
             total_COPING_waves == 8 ~ 8,
             total_COPING_waves == 9 ~ 9,
             total_COPING_waves == 10 ~ 10,
             total_COPING_waves == 11 ~ 11,
             total_COPING_waves == 12 ~ 12,
             total_COPING_waves == 13 ~ 13,
             total_COPING_waves == 14 ~ 14,
           ))

#Check new variable
glad_coping_participation %>% 
  group_by(total_COPING_waves_with0) %>% 
  count()
```

```{r Plot COPING surveys completed}
glad_coping_participation %>% 
  filter(total_COPING_waves != 0) %>% 
  ggplot(aes(x = total_COPING_waves)) +
  geom_bar(fill = glad_colour,
           colour = "black") +
  labs(#title = "Distribution of completed follow-up surveys amongst GLAD Study participants",
       #subtitle = paste0("No. of pt's who completed at least one follow-up: ", N_followups),
       #caption = paste0("No. of pt's completing no surveys: ", N_no_followups),
       y = "N",
       x = "No. of surveys completed") +
  scale_x_continuous(limits = c(NA, NA),
                   breaks = seq(1, 14, 1)) +
  scale_y_continuous(limits = c(0, 2000),
                     breaks = seq(0, 2000, 500)) +
  geom_text(aes(y = ..prop..,
                label = ..count..), 
            stat = "count",
            vjust = -1,
            nudge_y = .01) +
  theme_bw()
```

#Plots: Participation in the COPING baseline

Will create individual plots of demographic variables before combining them into
one plot. This includes:

- Age
- Gender
- Employment
- Ethnic identity

```{r Plot age within the GLAD sign up for baseline completion}

age_completed_baseline_plot <- glad_coping_participation %>% 
  ggplot(aes(x = age_groups_labelled, fill = completed_baseline_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Age (years)",
       y = "N participants") +
  scale_fill_manual(values = glad_coping_palette2) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Check plot
age_completed_baseline_plot

```

```{r Plot gender within the glad sign up for baseline completion}

gender_completed_baseline_plot <- glad_coping_participation %>% 
  filter(gender_recode_labelled != "Non-binary/prefer to self-define") %>% 
  ggplot(aes(x = gender_recode_labelled, fill = completed_baseline_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Gender",
       y = "N participants") +
  ylim(0, 20000) +
  scale_fill_manual(values = glad_coping_palette2) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))
  

#Check plot
gender_completed_baseline_plot

```

```{r Plot employment in the GLAD sign up for baseline completion}

employment_labels <- c(
  "Employed",
  "Retired",
  "Looking after home/family",
  "NA (disability/sickness)",
  "Unemployed",
  "Unpaid/voluntary work",
  "Student",
  "None"
)

employment_plot <- glad_coping_participation %>% 
  drop_na(employment_labelled) %>% 
  ggplot(aes(x = employment_labelled, fill = completed_baseline_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Employment status",
       y = "N participants") +
  scale_fill_manual(values = glad_coping_palette2) +
  scale_x_discrete(guide = guide_axis(n.dodge = 3),
                   labels = employment_labels) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Check plot
employment_plot

```

```{r Plot ethnicity in the GLAD sign up for baseline compeltion}

ethnicity_plot <- glad_coping_participation %>% 
  drop_na(ethnicity_labelled) %>% 
  ggplot(aes(x = ethnicity_labelled, fill = completed_baseline_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Ethnic identity",
       y = "N participants") +
  scale_fill_manual(values = glad_coping_palette2) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Check plot
ethnicity_plot

```

```{r Plot ethnic minorities in the GLAD sign up for baseline completion}

#Create ethnicity minority table grouped by COPING baseline completion status
ethnic_minortiy_COPING_baseline_table <- glad_coping_participation %>% 
  select(ethnicity_labelled, completed_baseline_labelled) %>% 
  filter(ethnicity_labelled != "White") %>% 
  group_by(ethnicity_labelled, completed_baseline_labelled) %>% 
  count()

#Create plot
ethnic_minority_plot <- ethnic_minortiy_COPING_baseline_table %>% 
  ggplot(aes(x = ethnicity_labelled, y = n, fill = completed_baseline_labelled)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Ethnic minority identity",
       y = "N participants") +
  ylim(0, 600) +
  scale_fill_manual(values = glad_coping_palette2) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme_classic() +
  theme(legend.position = "top",
        legend.margin = margin(0),
        legend.title = element_blank(),
        legend.text = element_text(size = 8.5)) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black")) +
       geom_text(aes(label = n), 
                 position = position_dodge(width=0.9), 
                 vjust=-0.25,
                 size = 3)

#Check plot
ethnic_minority_plot

```

##Create a combined plot

```{r Create plot layout matrix}

plot_layout_matrix <- matrix(c(1, 1, 2, 3, 3, 4), nrow = 2, byrow = TRUE)

#See matrix
plot_layout_matrix

```

```{r Create combined demograhics plot for baseline completion}

demographics_completed_baseline_plot <- grid.arrange(ethnic_minority_plot,
                                                     age_completed_baseline_plot,
                                                     employment_plot,
                                                     gender_completed_baseline_plot,
                                                     layout_matrix = plot_layout_matrix,
                                                     nrow = 2,
  bottom = textGrob("Non-binary/Self-defined: Did/Did not complete baseline (244; 457)", x = 1,
                            hjust = 1,
                            gp = gpar(fontface = 3L, fontsize = 9)))

```

#Plots: Participation in the COPING follow-ups

For the plots, we will use a categorical N COPING surveys variable instead 
of the full count variable. Following plots will be created and then merged:

- Age
- Gender
- Employment
- Ethnicity

```{r Create age plot for COPING follow-up completion}

age_group_COPING_waves_plot <- glad_coping_participation %>% 
  ggplot(aes(x = age_groups_labelled, fill = total_COPING_waves_binary_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Age (years)",
       y = "N participants") +
  scale_fill_manual(values = glad_coping_palette3) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Check plot
age_group_COPING_waves_plot

```

```{r Create Gender plot for COPING follow-up completion}

gender_COPING_waves_plot <- glad_coping_participation %>% 
  filter(gender_recode_labelled != "Non-binary/prefer to self-define") %>% 
  ggplot(aes(x = gender_recode_labelled, fill = total_COPING_waves_binary_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Gender",
       y = "N participants") +
  ylim(0, 20000) +
  scale_fill_manual(values = glad_coping_palette2) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Check plot
gender_COPING_waves_plot

```

```{r Create employment plot for COPING follow-up completion}

employment_COPING_waves_plot <- glad_coping_participation %>% 
  drop_na(employment_labelled) %>% 
  ggplot(aes(x = employment_labelled, fill = total_COPING_waves_binary_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Employment status",
       y = "N participants") +
  scale_fill_manual(values = glad_coping_palette2) +
  scale_x_discrete(guide = guide_axis(n.dodge = 3),
                   labels = employment_labels) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Check plot
employment_COPING_waves_plot

```

```{r Create ethnicity plot for COPING follow-up completion}

ethnicity_COPING_waves_plot <- glad_coping_participation %>% 
  drop_na(ethnicity_labelled) %>% 
  ggplot(aes(x = ethnicity_labelled, fill = total_COPING_waves_binary_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Ethnic identity",
       y = "N participants") +
  scale_fill_manual(values = glad_coping_palette2) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Check plot
ethnicity_COPING_waves_plot

```

```{r Create ethnic minorities plot for COPING follow-up completion}

#Get ethnic minority table grouped by total COPING waves group
ethnic_minortiy_COPING_followups_table <- glad_coping_participation %>% 
  select(ethnicity_labelled, total_COPING_waves_binary_labelled) %>% 
  filter(ethnicity_labelled != "White") %>% 
  group_by(ethnicity_labelled, total_COPING_waves_binary_labelled) %>% 
  count()

#Create ethnic minority/total COPING waves group plot
ethnic_minority_COPING_waves_plot <- ethnic_minortiy_COPING_followups_table %>% 
  ggplot(aes(x = ethnicity_labelled, y = n, fill = total_COPING_waves_binary_labelled)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Ethnic minority identity",
       y = "N participants") +
  scale_fill_manual(values = glad_coping_palette2) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black")) +
  theme(legend.position = "top",
        legend.margin = margin(0),
        legend.title = element_blank(),
        legend.text = element_text(size = 8.5)) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black")) +
       geom_text(aes(label = n), 
                 position = position_dodge(width=0.9), 
                 vjust=-0.25,
                 size = 3) +
  theme(plot.margin = margin(t = 10, unit = "pt")) + ## pad "t"op region of the plot
  coord_cartesian(clip = "off")

#Check plot
ethnic_minority_COPING_waves_plot

```

##Combined COPING waves participation plot

```{r Create plot layout matrix}

COPING_waves_layout_matrix <- matrix(c(1, 1, 2, 3, 3, 4), nrow = 2, byrow = TRUE)

#See matrix
COPING_waves_layout_matrix

```

```{r Create combined COPING waves participation plot}

demographics_COPING_waves_plot <- grid.arrange(ethnic_minority_COPING_waves_plot,
                                                     age_group_COPING_waves_plot,
                                                     employment_COPING_waves_plot,
                                                     gender_COPING_waves_plot,
                                                     layout_matrix = COPING_waves_layout_matrix,
                                                     nrow = 2)

```

#Summary tables

We want to caclucate/create three things:

- Descriptive statistics for continuous variables

- Create a table summarising the sociodemographic and psychiatric characteristics 
of those participants who did/didn't complete the COPING baseline

- Create a table summarising the sociodemographics and psychiatric characteristics 
of those participants who completed the follow-ups/baseline only participants

##Descriptive statistics

```{r Create vector of continuous variables}

continuous_variables <- c(
  "age_cleaned",
  "gad.sum_score",
  "phq.sum_score",
  "audit.sum_score",
  "MH_disorders_total_count"
)

```

```{r Calculate descriptive statistics for continous variables}

glad_coping_participation_desc <- glad_coping_participation %>% 
  select(all_of(continuous_variables),
         completed_baseline_labelled,
         total_COPING_waves_binary_labelled)

glad_coping_participation_desc %>% 
  summarise(across(all_of(continuous_variables),
                   list(m = mean,
                        std_d = sd),
                   na.rm = TRUE))

```

```{r Calculate descriptive statistics grouped by COPING baseline completion}

glad_coping_participation_desc %>% 
  group_by(completed_baseline_labelled) %>% 
  summarise(
    across(all_of(continuous_variables), 
           list(m = mean, 
                std_d = sd), 
           na.rm = TRUE)
    )

```

```{r Calculate descriptive statistics grouped by binary follow-up survey count}

glad_coping_participation_desc %>% 
  group_by(total_COPING_waves_binary_labelled) %>% 
  summarise(
    across(all_of(continuous_variables), 
           list(m = mean, 
                std_d = sd), 
           na.rm = TRUE)
    )

```

##COPING baseline participation table

```{r Add exclude cols for COPING baseline table plot}

COPING_baseline_table_variable_exclusions <- c(
  "sex_labelled",
  "depressive_disorder_labelled",
  "anxiety_disorder_labelled",
  "psychotic_disorder_labelled",
  "bipolar_disorder_labelled",
  "total_COPING_waves_labelled",
  "total_COPING_waves_binary_labelled"
)

```

```{r Get N counts for COPING baseline participation table}

#Note: Gender appears twice and sex also appears. Only gender should appear!
glad_coping_participation %>% 
  select(all_of(ends_with("_labelled"))) %>%
  select(-all_of(COPING_baseline_table_variable_exclusions)) %>% 
  tbl_summary(missing_text = "Missing",
              by = "completed_baseline_labelled")

```

##COPING follow-ups

```{r Add exclude cols for COPING baseline table plot}

COPING_waves_table_variable_exclusions <- c(
  "sex_labelled",
  "depressive_disorder_labelled",
  "anxiety_disorder_labelled",
  "psychotic_disorder_labelled",
  "bipolar_disorder_labelled",
  "age_groups_labelled",
  "joined_coping_first_invitation_labelled",
  #"depressive_and_anxiety_comorbidity_labelled",
  "personality_cluster_A_labelled",
  "personality_cluster_B_labelled",
  "personality_cluster_C_labelled",
  "mental_health_comorbidities_labelled",
  "completed_baseline_labelled",
  "total_COPING_waves_labelled"
)

```

```{r Filter for participants who completed the COPING baseline}

completed_COPING_baseline_pts <- glad_coping_participation %>% 
  filter(completed_baseline == 1)

```

```{r Get N and percentage values for COPING follow-ups}

completed_COPING_baseline_pts %>% 
  select(all_of(ends_with("_labelled"))) %>%
  select(-all_of(COPING_waves_table_variable_exclusions)) %>% 
  tbl_summary(missing_text = "Missing",
              by = "total_COPING_waves_binary_labelled")

```

#Correlations

```{r Calculate correlations}

correlation_vars <- c(
  "age_cleaned",
  "gender_recode",
  "highest_education",
  "dem.questions_based_ethnic_origin",
  "dem.what_is_your_current_employment_status",
  "dem.what_is_your_current_maritalrelationship_status",
  "phq.sum_score",
  "gad.sum_score",
  "audit.sum_score",
  "dem.select_the_box_that_best_describes_you",
  "physical_health_comorbidities",
  "MH_disorders_total_count",
  "depressive_and_anxiety_comorbidity",
  "eating_disorders",
  "OCRDs",
  "psychotic_and_biploar_disorder",
  "mhd.asd",
  "mhd.addadhd",
  "mhd.personality_disorder",
  "mhd.ptsd",
  "kit_returned",
  "completed_baseline",
  "total_COPING_waves"
)

#Select correlation variables
correlation_vars_data <- glad_coping_participation %>% 
  select(all_of(correlation_vars))

#Get correlations
all.corr.mat <- correlation_vars_data %>% 
  cor(use = "pairwise.complete.obs")

```

```{r Plot the correlations}

all.corr.mat %>% 
  corrplot(method = "color",
           addCoef.col = 1,
           number.cex = 0.3,
           tl.cex = 0.4,
           type = "lower")

```
