---
title: "Tables_and_plots"
author: "Steven Bright"
date: "22/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Clean global environment}

remove(list = ls())

```

#Call libraries

```{r Install packages}

#install.packages("cowplot")
#install.packages("grid")
#install.packages("gridExtra")
#install.packages("gtsummary")
#install.packages("corrplot")
#install.packages("polycor")
#install.packages("tidyverse")

```

```{r Load libraries}

library(cowplot)
library(grid)
library(gridExtra)
library(gtsummary)
library(corrplot)
library(polycor)
library(tidyverse)

```

#Add colour palette

```{r Create colour palettes}

glad_coping_palette2 <- c("#EFC10B", "#B7DEE8")
glad_coping_palette3 <- c("#EFC10B", "#B7DEE8", "#0403ff")

```

#Source functions

```{r Source functions}

source("..//COPING_participation_functions.r")

```

#Source data paths

```{r Source paths}

source("..//COPING_participation_paths.r")

```

```{r Read in glad coping participation data}

glad_coping_participation <- read_rds(paste0(processed_data_path, processed_data_name))

#Check data
glad_coping_participation %>% 
  head()

```

#Plots: Participation in the COPING baseline

Will create individual plots of demographic variables before combining them into
one plot. This includes:

- Age
- Gender
- Employment
- Ethnic identity

```{r Plot age within the GLAD sign up for baseline completion}

age_completed_baseline_plot <- glad_coping_participation %>% 
  ggplot(aes(x = age_groups_labelled, fill = completed_baseline_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Age (years)",
       y = "N participants") +
  scale_fill_manual(values = glad_coping_palette2) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Check plot
age_completed_baseline_plot

```

```{r Plot gender within the glad sign up for baseline completion}

gender_completed_baseline_plot <- glad_coping_participation %>% 
  filter(gender_recode_labelled != "Non-binary/prefer to self-define") %>% 
  ggplot(aes(x = gender_recode_labelled, fill = completed_baseline_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Gender",
       y = "N participants") +
  ylim(0, 20000) +
  scale_fill_manual(values = glad_coping_palette2) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))
  

#Check plot
gender_completed_baseline_plot

```

```{r Plot employment in the GLAD sign up for baseline completion}

employment_labels <- c(
  "Employed",
  "Retired",
  "Looking after home/family",
  "NA (disability/sickness)",
  "Unemployed",
  "Unpaid/voluntary work",
  "Student",
  "None"
)

employment_plot <- glad_coping_participation %>% 
  drop_na(employment_labelled) %>% 
  ggplot(aes(x = employment_labelled, fill = completed_baseline_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Employment status",
       y = "N participants") +
  scale_fill_manual(values = glad_coping_palette2) +
  scale_x_discrete(guide = guide_axis(n.dodge = 3),
                   labels = employment_labels) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Check plot
employment_plot

```

```{r Plot ethnicity in the GLAD sign up for baseline compeltion}

ethnicity_plot <- glad_coping_participation %>% 
  drop_na(ethnicity_labelled) %>% 
  ggplot(aes(x = ethnicity_labelled, fill = completed_baseline_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Ethnic identity",
       y = "N participants") +
  scale_fill_manual(values = glad_coping_palette2) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Check plot
ethnicity_plot

```

```{r Plot ethnic minorities in the GLAD sign up for baseline completion}

#Create ethnicity minority table grouped by COPING baseline completion status
ethnic_minortiy_COPING_baseline_table <- glad_coping_participation %>% 
  select(ethnicity_labelled, completed_baseline_labelled) %>% 
  filter(ethnicity_labelled != "White") %>% 
  group_by(ethnicity_labelled, completed_baseline_labelled) %>% 
  count()

#Create plot
ethnic_minority_plot <- ethnic_minortiy_COPING_baseline_table %>% 
  ggplot(aes(x = ethnicity_labelled, y = n, fill = completed_baseline_labelled)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Ethnic minority identity",
       y = "N participants") +
  ylim(0, 600) +
  scale_fill_manual(values = glad_coping_palette2) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme_classic() +
  theme(legend.position = "top",
        legend.margin = margin(0),
        legend.title = element_blank(),
        legend.text = element_text(size = 8.5)) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black")) +
       geom_text(aes(label = n), 
                 position = position_dodge(width=0.9), 
                 vjust=-0.25,
                 size = 3)

#Check plot
ethnic_minority_plot

```

##Create a combined plot

```{r Create plot layout matrix}

plot_layout_matrix <- matrix(c(1, 1, 2, 3, 3, 4), nrow = 2, byrow = TRUE)

#See matrix
plot_layout_matrix

```

```{r Create combined demograhics plot for baseline completion}

demographics_completed_baseline_plot <- grid.arrange(ethnic_minority_plot,
                                                     age_completed_baseline_plot,
                                                     employment_plot,
                                                     gender_completed_baseline_plot,
                                                     layout_matrix = plot_layout_matrix,
                                                     nrow = 2,
  bottom = textGrob("Non-binary/Self-defined: Did/Did not complete baseline (244; 457)", x = 1,
                            hjust = 1,
                            gp = gpar(fontface = 3L, fontsize = 9)))

```

#Plots: Participation in the COPING follow-ups

For the plots, we will use a categorical N COPING surveys variable instead 
of the full count variable. Following plots will be created and then merged:

- Age
- Gender
- Employment
- Ethnicity

```{r Create age plot for COPING follow-up completion}

age_group_COPING_waves_plot <- glad_coping_participation %>% 
  ggplot(aes(x = age_groups_labelled, fill = total_COPING_waves_binary_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Age (years)",
       y = "N participants") +
  scale_fill_manual(values = glad_coping_palette3) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Check plot
age_group_COPING_waves_plot

```

```{r Create Gender plot for COPING follow-up completion}

gender_COPING_waves_plot <- glad_coping_participation %>% 
  filter(gender_recode_labelled != "Non-binary/prefer to self-define") %>% 
  ggplot(aes(x = gender_recode_labelled, fill = total_COPING_waves_binary_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Gender",
       y = "N participants") +
  ylim(0, 20000) +
  scale_fill_manual(values = glad_coping_palette2) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Check plot
gender_COPING_waves_plot

```

```{r Create employment plot for COPING follow-up completion}

employment_COPING_waves_plot <- glad_coping_participation %>% 
  drop_na(employment_labelled) %>% 
  ggplot(aes(x = employment_labelled, fill = total_COPING_waves_binary_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Employment status",
       y = "N participants") +
  scale_fill_manual(values = glad_coping_palette2) +
  scale_x_discrete(guide = guide_axis(n.dodge = 3),
                   labels = employment_labels) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Check plot
employment_COPING_waves_plot

```

```{r Create ethnicity plot for COPING follow-up completion}

ethnicity_COPING_waves_plot <- glad_coping_participation %>% 
  drop_na(ethnicity_labelled) %>% 
  ggplot(aes(x = ethnicity_labelled, fill = total_COPING_waves_binary_labelled)) +
  geom_bar(position = "dodge") +
  labs(x = "Ethnic identity",
       y = "N participants") +
  scale_fill_manual(values = glad_coping_palette2) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Check plot
ethnicity_COPING_waves_plot

```

```{r Create ethnic minorities plot for COPING follow-up completion}

#Get ethnic minority table grouped by total COPING waves group
ethnic_minortiy_COPING_followups_table <- glad_coping_participation %>% 
  select(ethnicity_labelled, total_COPING_waves_binary_labelled) %>% 
  filter(ethnicity_labelled != "White") %>% 
  group_by(ethnicity_labelled, total_COPING_waves_binary_labelled) %>% 
  count()

#Create ethnic minority/total COPING waves group plot
ethnic_minority_COPING_waves_plot <- ethnic_minortiy_COPING_followups_table %>% 
  ggplot(aes(x = ethnicity_labelled, y = n, fill = total_COPING_waves_binary_labelled)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Ethnic minority identity",
       y = "N participants") +
  scale_fill_manual(values = glad_coping_palette2) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme_classic() +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black")) +
  theme(legend.position = "top",
        legend.margin = margin(0),
        legend.title = element_blank(),
        legend.text = element_text(size = 8.5)) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black")) +
       geom_text(aes(label = n), 
                 position = position_dodge(width=0.9), 
                 vjust=-0.25,
                 size = 3) +
  theme(plot.margin = margin(t = 10, unit = "pt")) + ## pad "t"op region of the plot
  coord_cartesian(clip = "off")

#Check plot
ethnic_minority_COPING_waves_plot

```

##Combined COPING waves participation plot

```{r Create plot layout matrix}

COPING_waves_layout_matrix <- matrix(c(1, 1, 2, 3, 3, 4), nrow = 2, byrow = TRUE)

#See matrix
COPING_waves_layout_matrix

```

```{r Create combined COPING waves participation plot}

demographics_COPING_waves_plot <- grid.arrange(ethnic_minority_COPING_waves_plot,
                                                     age_group_COPING_waves_plot,
                                                     employment_COPING_waves_plot,
                                                     gender_COPING_waves_plot,
                                                     layout_matrix = COPING_waves_layout_matrix,
                                                     nrow = 2)

```

#Summary tables

We want to caclucate/create three things:

- Descriptive statistics for continuous variables

- Create a table summarising the sociodemographic and psychiatric characteristics 
of those participants who did/didn't complete the COPING baseline

- Create a table summarising the sociodemographics and psychiatric characteristics 
of those participants who completed the follow-ups/baseline only participants

##Descriptive statistics

```{r Calculate descriptive statistics for continous variables}

glad_coping_participation_desc <- glad_coping_participation %>% 
  select(age_cleaned,
         gad.sum_score,
         phq.sum_score,
         audit.sum_score)

glad_coping_participation_desc %>% 
  map(function(x){
    mean_v = mean(x)
    standard_d = sd(x)
    return(list(mean = mean_v, sd = standard_d))
  })

```


##COPING baseline participation table

```{r Add exclude cols for COPING baseline table plot}

COPING_baseline_table_variable_exclusions <- c(
  "sex_labelled",
  "depressive_disorder_labelled",
  "anxiety_disorder_labelled",
  "psychotic_disorder_labelled",
  "bipolar_disorder_labelled",
  "total_COPING_waves_labelled",
  "total_COPING_waves_binary_labelled"
)

```

```{r Get N counts for COPING baseline participation table}

#Note: Gender appears twice and sex also appears. Only gender should appear!
glad_coping_participation %>% 
  select(all_of(ends_with("_labelled"))) %>%
  select(-all_of(COPING_baseline_table_variable_exclusions)) %>% 
  tbl_summary(missing_text = "Missing",
              by = "completed_baseline_labelled")

```

##COPING follow-ups

```{r Add exclude cols for COPING baseline table plot}

COPING_waves_table_variable_exclusions <- c(
  "sex_labelled",
  "depressive_disorder_labelled",
  "anxiety_disorder_labelled",
  "psychotic_disorder_labelled",
  "bipolar_disorder_labelled",
  "completed_baseline_labelled",
  "total_COPING_waves_labelled"
)

```

```{r Filter for participants who completed the COPING baseline}

completed_COPING_baseline_pts <- glad_coping_participation %>% 
  filter(completed_baseline == 1)

```

```{r Get N and percentage values for COPING follow-ups}

completed_COPING_baseline_pts %>% 
  select(all_of(ends_with("_labelled"))) %>%
  select(-all_of(COPING_waves_table_variable_exclusions)) %>% 
  tbl_summary(missing_text = "Missing",
              by = "total_COPING_waves_binary_labelled")

```

#Correlation matrices

```{r Create correlation matrix for sociodemographic variables}

#Create character vector of sociodemographic variables
sociodemographic_variable_names <- c(
  "age_cleaned",
  "gender_recode",
  "highest_education",
  "dem.questions_based_ethnic_origin",
  "dem.what_is_your_current_employment_status",
  "dem.what_is_your_current_maritalrelationship_status",
  "kit_returned",
  "joined_coping_first_invitation"
)

#Select correlation variables
sociodemographic_correlation_vars <- glad_coping_participation %>% 
  select(all_of(sociodemographic_variable_names))

#Get correlations
all.corr.mat_sociodemographic <- sociodemographic_correlation_vars %>% 
  hetcor(use = "pairwise.complete.obs")

```

```{r Save cormat as a matrix object}

all.corr.matrix_sociodemographic <- as.matrix(all.corr.mat_sociodemographic)

```

```{r Save p values}

all.p.matrix_sociodemographic <- as.matrix(all.corr.mat_sociodemographic$tests)

```

```{r Create correlation plot for sociodemographic variables}

all.corr.matrix_sociodemographic %>%
  corrplot(method = "color", # objects to represent the correlations on plot
         type = "lower", # only use the lower triangle of the matrix
         diag = FALSE, # do not show the correlations on the diagonal
         addgrid.col = NA,
         addCoef.col = "black", # colour for the correlation coefficients in the plot
         tl.cex = 0.7, #size of text
         tl.col = "black",
         col=colorRampPalette(c("dodgerblue4",
                                "white",
                                "firebrick4"))(200), # colours for correlations
         # Combine with significance
         p.mat = all.p.matrix_sociodemographic, # Matrix with p values
         sig.level = 0.01, # Choose significant level
         insig = "blank") # Nonsignificant correlations have no colour

```

###Psychiatric and health correlation matrix

```{r Get the correlations for the psychiatric and health vars}

#Create character vector of psychiatric and health variables
psychiatric_and_health_variable_names <- c(
  "phq.sum_score",
  "gad.sum_score",
  "audit.sum_score",
  "dem.select_the_box_that_best_describes_you",
  "physical_health_comorbidities",
  "mental_health_comorbidities",
  "depressive_and_anxiety_comorbidity",
  "eating_disorders",
  "OCRDs",
  "psychotic_and_biploar_disorder",
  "mhd.asd",
  "mhd.addadhd",
  "mhd.personality_disorder"
)

#Select correlation variables
psychiatric_and_health_correlation_vars <- glad_coping_participation %>% 
  select(all_of(psychiatric_and_health_variable_names))

#Get correlations
all.corr.mat_psychatric_and_health <- psychiatric_and_health_correlation_vars %>% 
  hetcor(use = "pairwise.complete.obs")

```

```{r Save cormat as a matrix object}

all.corr.matrix_psychiatric_and_health <- as.matrix(all.corr.mat_psychatric_and_health)

```

```{r Save p values}

all.p.matrix_psychiatric_and_health <- as.matrix(all.corr.mat_psychatric_and_health$tests)

```

```{r Create correlation plot for psychiatric and health variables}

all.corr.matrix_psychiatric_and_health %>%
  corrplot(method = "color", # objects to represent the correlations on plot
         type = "lower", # only use the lower triangle of the matrix
         diag = FALSE, # do not show the correlations on the diagonal
         addgrid.col = NA,
         addCoef.col = "black", # colour for the correlation coefficients in the plot
         tl.cex = 0.7, #size of text
         tl.col = "black",
         col=colorRampPalette(c("dodgerblue4",
                                "white",
                                "firebrick4"))(200), # colours for correlations
         # Combine with significance
         p.mat = all.p.matrix_psychiatric_and_health, # Matrix with p values
         sig.level = 0.01, # Choose significant level
         insig = "blank") # Nonsignificant correlations have no colour

```

#Testing 

```{r Correlation variables}

correlation_vars <- c(
  "age_cleaned",
  "gender_recode",
  "highest_education",
  "dem.questions_based_ethnic_origin",
  "dem.what_is_your_current_employment_status",
  "dem.what_is_your_current_maritalrelationship_status",
  "kit_returned",
  "joined_coping_first_invitation",
  "phq.sum_score",
  "gad.sum_score",
  "audit.sum_score",
  "dem.select_the_box_that_best_describes_you",
  "physical_health_comorbidities",
  "mental_health_comorbidities",
  "depressive_and_anxiety_comorbidity",
  "eating_disorders",
  "OCRDs",
  "psychotic_and_biploar_disorder",
  "mhd.ptsd",
  "mhd.asd",
  "mhd.addadhd",
  "mhd.personality_disorder"
)

#Select correlation variables
correlation_vars_data <- glad_coping_participation %>% 
  select(all_of(correlation_vars))

#Get correlations
all.corr.mat <- correlation_vars_data %>% 
  hetcor(use = "pairwise.complete.obs")

```

```{r Save cormat as a matrix object}

all.corr.matrix <- as.matrix(all.corr.mat)

```

```{r Save p values}

all.p.matrix <- as.matrix(all.corr.mat$tests)

```

```{r Create corrplot of all variables}

all.corr.matrix %>%
  corrplot(method = "color", # objects to represent the correlations on plot
         type = "lower", # only use the lower triangle of the matrix
         diag = FALSE, # do not show the correlations on the diagonal
         addgrid.col = NA,
         addCoef.col = "black", # colour for the correlation coefficients in the plot
         tl.cex = 0.5, #size of text
         number.cex = 0.5,
         tl.col = "black",
         col=colorRampPalette(c("dodgerblue4",
                                "white",
                                "firebrick4"))(200), # colours for correlations
         # Combine with significance
         p.mat = all.p.matrix, # Matrix with p values
         sig.level = 0.01, # Choose significant level
         insig = "blank")

```
